---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# countByGeneral

<!-- badges: start -->
<!-- badges: end -->

The `countByGeneral` package provides a flexible way to group and summarize data in R. It is particularly useful when dealing with categorical data where entries may include commas or when summarizing date fields by year.

## Description

The main function `count_by_general()` groups data by one or more specified categorical variables and returns a summary tibble. For each specified column, only the part before any comma is kept. If a date column is specified, only the year part of the date is used.

## Installation

You can install the development version of `countByGeneral` from GitHub with:

```{r}
# install.packages("devtools")
devtools::install_github("https://github.com/stat545ubc-2023/countByGeneral.git", upgrade = "never", force = TRUE)
```

## Examples

Using the steam_games dataset for the data parameter.

Here will show how the function works when only one categorical variable(genre) is used for the parameter column_names.

```{r example}
library(countByGeneral)
library(datateachr)
summary_result <- count_by_general(steam_games, "genre")
summary_result
```

The function also works when column_names is a character vector containing the names of two categorical grouping variables (genre, languages).

```{r example 2}
library(countByGeneral)
library(datateachr)
summary_result <- count_by_general(steam_games, c("genre", "languages"))
summary_result

```

